---
title: "IsolateGrowthCurves"
author: "Venus Kuo"
date: "September 11, 2017"
output: html_document
---

# 1) Questions

- Does Rpf+ treatment to soil increase the cultivation of Rpf-responders? 

## Methods

I performed 72 hour growth curve assay with Rpf+/Rpf- treatment on 38 soil isolates that appeared on plates Rpf treated plates in the GPCA project but not on the Rpf- control plates. I then extracted the growth curve parameters using the modified gompertz r code from the lennon lab repo and quantified the relative change in growth curve parameters with Rpf treatment.


# 2) Set working environment and load packages

```{r setup}
# Set working directory #
rm(list = ls())
getwd()
setwd("~/../GitHub/DormancyGPCA/data/")

# Require or install packages #
package.list <- c('vegan', 'ggplot2','plyr') 
for (package in package.list) {
  if (!require(package, character.only=T, quietly=T)) { 
    install.packages(package)
    library(package, character.only=T)
} }
```


# 3) Load growth curve parameter data 

Imported growth curve parameter output from Modified Gompertz growth curve code

```{r}
setwd("~/../GitHub/DormancyGPCA/data/")
# Import Growth Rate Data 
#gc <- read.table("isolate.gc.1.txt", sep = "\t", header = TRUE, row.names = 1)
gc <- read.table("isolate.gc.2.txt", sep="\t", header= TRUE, row.names = 1)


# Subset the gc data set
growth <- subset(gc, select = c("A", "umax", "L", "isolate", "treatment", "rep"))

# Make Isolate factors 
growth$isolate <- as.factor(growth$isolate)
```


# 4) Visualizing the effects of Rpf treatment on soil isolate growth parameters

```{r}
# Lag time # 
# Calculating the mean and sem of replicates of each isolate and treatment group 
growth.L.sem <- ddply(growth, c("isolate", "treatment"), summarise, 
                   mean=mean(L), sem=sd(L)/sqrt(length(L)))
growth.L.sem <- transform(growth.L.sem, lower=mean-sem, upper=mean+sem) 
# Bargraph of treatment and isolate group 
growth.L.bar <- ggplot(growth.L.sem, aes(x=isolate, y = mean, fill=treatment)) + 
  geom_bar(width=0.5, colour="black", position = position_dodge(width = 0.65), stat = "identity", size=1)  
# Nice Figure
growth.L.bar + geom_errorbar(aes(ymax=upper, ymin=lower),
                              position=position_dodge(0.65), data=growth.L.sem, width = 0.2, size = 1) +
  labs(x="Soil Isolates", y="Lag Time") +
  scale_fill_manual(values=c("Black", "White")) +
  theme_classic() +
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.text.x=element_text(colour="black", size =18),
        axis.title=element_text(size=22),
        axis.title.y = element_text(colour="black",  margin = margin(0,10,0,10)),
        axis.title.x = element_text(colour="black",margin=margin(5,0,0,0)),
        panel.border = element_rect(linetype = "solid", colour = "black", size=3, fill=NA),
        axis.ticks.length = unit(.25, "cm"),
        axis.ticks = element_line(size = 2),
        legend.title = element_text(size=18),
        legend.text=element_text(size=18))

# Maximum growth rate # 
growth.umax.sem <- ddply(growth, c("isolate", "treatment"), summarise, 
                   mean=mean(umax), sem=sd(umax)/sqrt(length(umax)))
growth.umax.sem <- transform(growth.umax.sem, lower=mean-sem, upper=mean+sem) 
growth.umax.bar <- ggplot(growth.umax.sem, aes(x=isolate, y = mean, fill=treatment)) + 
  geom_bar(width=0.5, colour="black", position = position_dodge(width = 0.65), stat = "identity", size=1)  
growth.umax.bar + geom_errorbar(aes(ymax=upper, ymin=lower),
                              position=position_dodge(0.65), data=growth.umax.sem, width = 0.2, size = 1) +
  labs(x="Soil Isolates", y="Maximum growth rate") +
  scale_fill_manual(values=c("Black", "White")) +
  theme_classic() +
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.text.x=element_text(colour="black", size =18),
        axis.title=element_text(size=22),
        axis.title.y = element_text(colour="black",  margin = margin(0,10,0,10)),
        axis.title.x = element_text(colour="black",margin=margin(5,0,0,0)),
        panel.border = element_rect(linetype = "solid", colour = "black", size=3, fill=NA),
        axis.ticks.length = unit(.25, "cm"),
        axis.ticks = element_line(size = 2),
        legend.title = element_text(size=18),
        legend.text=element_text(size=18))

# Biomass yeild # 
growth.A.sem <- ddply(growth, c("isolate", "treatment"), summarise, 
                   mean=mean(A), sem=sd(A)/sqrt(length(A)))
growth.A.sem <- transform(growth.A.sem, lower=mean-sem, upper=mean+sem) 
growth.A.bar <- ggplot(growth.A.sem, aes(x=isolate, y = mean, fill=treatment)) + 
  geom_bar(width=0.5, colour="black", position = position_dodge(width = 0.65), stat = "identity", size=1)  
growth.A.bar + geom_errorbar(aes(ymax=upper, ymin=lower),
                              position=position_dodge(0.65), data=growth.A.sem, width = 0.2, size = 1) +
  labs(x="Soil Isolates", y="Biomass Yeild (OD600)") +
  scale_fill_manual(values=c("Black", "White")) +
  theme_classic() +
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.text.x=element_text(colour="black", size =18),
        axis.title=element_text(size=22),
        axis.title.y = element_text(colour="black",  margin = margin(0,10,0,10)),
        axis.title.x = element_text(colour="black",margin=margin(5,0,0,0)),
        panel.border = element_rect(linetype = "solid", colour = "black", size=3, fill=NA),
        axis.ticks.length = unit(.25, "cm"),
        axis.ticks = element_line(size = 2),
        legend.title = element_text(size=18),
        legend.text=element_text(size=18))
```


# 5) Statistics

```{r}
# Maximum growth rate # 
# Two factor ANOVA # 
umax.aov <- aov(umax ~ treatment+isolate+treatment*isolate, data=growth)
summary(umax.aov)
umax.aov <- aov(umax ~ treatment, data=growth)
summary(umax.aov)
TukeyHSD(umax.aov)
# The interactive effect of treatment and isolate is significant on umax F5,36 = 36.46, p < 0.0001 #

# Lag time to exponential growth # 
# Two factor ANOVA # 
L.aov <- aov(L ~ treatment+isolate+treatment*isolate, data=growth)
summary(L.aov)
L.aov <- aov(L ~ treatment, data=growth)
summary(L.aov)
TukeyHSD(L.aov)
# The interactive effect of treatment and isolate is significant on lag time F5,36 = 9.226, p < 0.001 #

# Final biomass yeild # 
# Two factor ANOVA # 
A.aov <- aov(A ~ treatment+isolate+treatment*isolate, data=growth)
summary(A.aov)
A.aov <- aov(A ~ treatment, data=growth)
summary(A.aov)
TukeyHSD(A.aov)
# The interactive effect of treatment and isolate is significant on biomass yeild F5,36 = 4.056, p = 0.005 #
```


# 6) Proportional differences for each isolate between two treatment groups # 

```{r}
# Make subset of each treatment group
Rpf <- subset(growth, treatment == "Rpf+")
control <- subset(growth, treatment == "Rpf-")

# Order the two dataset by isolate and rep number 
Rpf <- with(Rpf, Rpf[order(isolate,rep),])
control <- with(control, control[order(isolate,rep),])

# New data frame to input proportional difference with treatment
m <- matrix(0, ncol = 0, nrow = 22)
data <- as.data.frame(m)

# Set vectors as growth parameters 
control.A <- control$A
Rpf.A <- Rpf$A
control.umax <- control$umax
Rpf.umax <- Rpf$umax
control.L <- control$L
Rpf.L <- Rpf$L

# Populate data frame with % change with Rpf treatment
data$A <- ((Rpf.A-control.A)/control.A)*100
data$L <- ((Rpf.L-control.L)/control.L)*100
data$umax <- ((Rpf.umax-control.umax)/control.umax)*100
data$isolate <- Rpf$isolate
data$rep <- Rpf$rep

# Plot box plot to quickly visualize changes
boxplot(A ~ isolate, data=data, main="Biomass")
boxplot(umax ~ isolate, data=data, main="Umax")
boxplot(L ~ isolate, data=data, main="Lag")

```







