---
title: "DormancyGPCA - NegativeControl"
author: "Venus Kuo"
date: "September 25, 2017"
output: html_document
---

# 1) Questions

1. We test whether Rpf muralytic activity is necessary for inducing Rpf effects on soil bacterial diversity and abundance. 


# 2) Set working environment and load packages

```{r setup}
# Set working directory #
rm(list = ls())
getwd()
setwd("~/../GitHub/DormancyGPCA/data/")

# Require or install packages #
package.list <- c('vegan', 'ggplot2', 'gplots', 'plyr', 'psych', 'corrplot', 'BiodiversityR', 'RColorBrewer') 
for (package in package.list) {
  if (!require(package, character.only=T, quietly=T)) { 
    install.packages(package)
    library(package, character.only=T)
} }
```


# 3) Load and describe data set

Negativecontrol.txt: 

Data modification:
1. 

```{r}
setwd("~/../GitHub/DormancyGPCA/data/")
# Load cfu.csv dataset #
cfu <- read.csv("Negativecontrol.txt",  header=T)

# Remove NAs # 
cfu <- na.omit(cfu)

# Calculating and standardizing CFU # 
dil.factor <- cfu$Dilution
soilamount <- cfu$Soil
cfu$CFU <- cfu$Colonies/dil.factor
cfu$stdCFU <- (cfu$CFU)/soilamount
cfu$stdcfu.log<- log10(cfu$stdCFU) 

# Standardizing morphotype # 
cfu$stdMorph <- (cfu$Morphotypes/soilamount)
cfu$stdMorph.log <- log10(cfu$stdMorph)

# Look at the data set # 
#View(cfu)
```


# 4) Visualizing CFU and morphology with Rpf treatment

## Visualization of CFU/Soil(g) bar plot 

```{r}
# Average of each treatment by sample # 
cfu.mean <- ddply(cfu, c("Treatment"), summarise, 
                   mean=mean(stdCFU), sem=sd(stdCFU)/sqrt(length(stdCFU)))
cfu.mean <- transform(cfu.mean, lower=mean-sem, upper=mean+sem) 

# Bar graph CFU # 
cfu.bar<- ggplot(data = cfu.mean, aes(x=Treatment,y = mean)) + 
  geom_bar(width=0.5, colour="black", position = position_dodge(width = 0.65), stat = "identity", size=1)  


cfu.plot <- cfu.bar +    # Figure editting #
  labs(x="Treatment groups", 
       y="CFU/Soil(g)") +
  geom_errorbar(aes(ymax=upper, ymin=lower), data=cfu.mean, width = 0.25, size = 0.75) +
  theme_classic() +
  theme(axis.text.y=element_text(colour="black", size=20, margin =margin(0,15,0,0)),
        axis.text.x=element_text(colour="black", size =20, margin =margin(15,0,0,0)),
        axis.title.y = element_text(colour="black", size=20,  margin = margin(0,20,0,10)),
        axis.title.x = element_text(colour="black", size=20,  margin=margin(20,0,0,0)),
        panel.border = element_rect(linetype = "solid", colour = "black", size=3, fill=NA),
        axis.ticks.length = unit(-0.35, "cm"),
        axis.ticks = element_line(size = 1.65, colour="black"),
        legend.title = element_text(size=15),
        legend.text=element_text(size=15))  + 
  annotate("text", x =0.6, y=225000000, label = c("A"), size=12)

cfu.plot
```


## Visualization of Morphotype/Soil(g) bar plot 

```{r}
# Average of each treatment by sample # 
uniq.mean <- ddply(cfu, c("Treatment"), summarise, 
                   mean=mean(stdMorph), sem=sd(stdMorph)/sqrt(length(stdMorph)))
uniq.mean <- transform(uniq.mean, lower=mean-sem, upper=mean+sem) 

# Bar graph CFU # 
uniq.bar <- ggplot(data = uniq.mean, aes(x=Treatment,y = mean)) + 
  geom_bar(width=0.5, colour="black", position = position_dodge(width = 0.65), stat = "identity", size=1)  

# Polished Figures # 
uniq.plot <- uniq.bar +    # Figure editting #
  labs(y="Morphotype/Soil(g)") +
  geom_errorbar(aes(ymax=upper, ymin=lower), data=uniq.mean, width = 0.25, size = 0.75) +
  theme_classic() +
  theme(axis.title.x=element_blank(),
        axis.text.y=element_text(colour="black", size=20, margin =margin(0,15,0,0)),
        axis.text.x=element_text(colour="black", size =20, margin =margin(15,0,0,0)),
        axis.title.y = element_text(colour="black", size=20,  margin = margin(0,20,0,10)),
        panel.border = element_rect(linetype = "solid", colour = "black", size=3, fill=NA),
        axis.ticks.length = unit(-0.35, "cm"),
        axis.ticks = element_line(size = 1.65, colour="black"),
        legend.title = element_text(size=15),
        legend.text=element_text(size=15)) #+ 
  #annotate("text", x =0.6, y=37, label = c("B"), size=12)

uniq.plot  # Plot #
```


# 5) Does treatment type affect CFU and morphotype counts?

```{r}
# Rpf effect on CFU #  
neg.cfu.aov <- aov(stdCFU ~ Treatment, data=cfu)
summary(neg.cfu.aov)
TukeyHSD(neg.cfu.aov)

# Rpf effect on morphotype # 
neg.morp.aov <- aov(stdMorph ~ Treatment, data=cfu)
summary(neg.morp.aov)
TukeyHSD(neg.morp.aov)
```




