---
title: "DormancyGPCA - NegativeControl"
author: "Venus Kuo"
date: "September 25, 2017"
output: html_document
---

# 1) Questions

We test whether a concentration gradent of Rpf can affect the diversity and abundance of soil microbial community on agar plates.

Soil was extracted from Dunn woods over the course of months, treated to a gradient of Rpf concentrations (umol/L) for 3 days before vortexed in pyrophosphate solution and spread plated on R2A plates infused with cycloheximide. Colony forming units (CFU) and distinct morphological (unique) colony were counted by eye on plate counter. 


# 2) Set working environment and load packages

```{r setup}
# Set working directory #
rm(list = ls())
getwd()
setwd("~/../GitHub/DormancyGPCA/data/")

# Require or install packages #
package.list <- c('vegan', 'ggplot2', 'gplots', 'plyr', 'psych', 'corrplot', 'BiodiversityR', 'RColorBrewer') 
for (package in package.list) {
  if (!require(package, character.only=T, quietly=T)) { 
    install.packages(package)
    library(package, character.only=T)
} }
```


# 3) Load and describe data set

plateCfuMorphotypeData.txt : A text file containing the sample location, treatment concentration, replicate number, dilution factor, colony counts, and morphology counts. 

Below, I calulated CFU based on colony counts and dilution factor. I standardized the CFU and morphotype counts by soil amount (g). CFU was log10 transformed to look at the magnitude of CFU changes with Rpf treatment. The Rpf treatment concentration was natural log transformed due to uneven concentration treatments. 

```{r}
setwd("~/../GitHub/DormancyGPCA/data/")
# Load cfu.csv dataset #
cfu <- read.csv("Negativecontrol.txt",  header=T)

# Remove NAs # 
cfu <- na.omit(cfu)

# Calculating and standardizing CFU # 
dil.factor <- cfu$Dilution
soilamount <- cfu$Soil
cfu$CFU <- cfu$Colonies/dil.factor
cfu$stdCFU <- (cfu$CFU)/soilamount
cfu$stdcfu.log<- log10(cfu$stdCFU) 

# Standardizing morphotype # 
cfu$stdMorph <- (cfu$Morphotypes/soilamount)
cfu$stdMorph.log <- log10(cfu$stdMorph)

# Look at the data set # 
#View(cfu)
```


# 4) Visualizing CFU and morphology with Rpf treatment

## Visualization of CFU/Soil(g) bar plot 

```{r}
# Average of each treatment by sample # 
cfu.mean <- ddply(cfu, c("Treatment"), summarise, 
                   mean=mean(stdCFU), sem=sd(stdCFU)/sqrt(length(stdCFU)))
cfu.mean <- transform(cfu.mean, lower=mean-sem, upper=mean+sem) 

# Bar graph CFU # 
cfu.bar<- ggplot(data = cfu.mean, aes(x=Treatment,y = mean)) + 
  geom_bar(width=0.5, colour="black", position = position_dodge(width = 0.65), stat = "identity", size=1)  


cfu.plot <- cfu.bar +    # Figure editting #
  labs(x="Treatment groups", 
       y="CFU/Soil(g)") +
  geom_errorbar(aes(ymax=upper, ymin=lower), data=cfu.mean, width = 0.1, size = 0.5) +
  theme_classic() +
  theme(axis.text.y=element_text(colour="black", size=20, margin =margin(0,15,0,0)),
        axis.text.x=element_text(colour="black", size =20, margin =margin(15,0,0,0)),
        axis.title.y = element_text(colour="black", size=20,  margin = margin(0,20,0,10)),
        axis.title.x = element_text(colour="black", size=20,  margin=margin(20,0,0,0)),
        panel.border = element_rect(linetype = "solid", colour = "black", size=3, fill=NA),
        axis.ticks.length = unit(-0.35, "cm"),
        axis.ticks = element_line(size = 1.65, colour="black"),
        legend.title = element_text(size=15),
        legend.text=element_text(size=15))  #+ 
  #annotate("text", x =0.6, y=9.25, label = c("a"), size=12)

cfu.plot
```


## Visualization of Morphotype/Soil(g) bar plot 

```{r}
# Average of each treatment by sample # 
uniq.mean <- ddply(cfu, c("Treatment"), summarise, 
                   mean=mean(stdMorph), sem=sd(stdMorph)/sqrt(length(stdMorph)))
uniq.mean <- transform(uniq.mean, lower=mean-sem, upper=mean+sem) 

# Bar graph CFU # 
uniq.bar <- ggplot(data = uniq.mean, aes(x=Treatment,y = mean)) + 
  geom_bar(width=0.5, colour="black", position = position_dodge(width = 0.65), stat = "identity", size=1)  

# Polished Figures # 
uniq.plot <- uniq.bar +    # Figure editting #
  labs(x="Treatment groups", 
       y="Morphotype/Soil(g)") +
  geom_errorbar(aes(ymax=upper, ymin=lower), data=uniq.mean, width = 0.1, size = 0.5) +
  theme_classic() +
  theme(axis.text.y=element_text(colour="black", size=20, margin =margin(0,15,0,0)),
        axis.text.x=element_text(colour="black", size =20, margin =margin(15,0,0,0)),
        axis.title.y = element_text(colour="black", size=20,  margin = margin(0,20,0,10)),
        axis.title.x = element_text(colour="black", size=20,  margin=margin(20,0,0,0)),
        panel.border = element_rect(linetype = "solid", colour = "black", size=3, fill=NA),
        axis.ticks.length = unit(-0.35, "cm"),
        axis.ticks = element_line(size = 1.65, colour="black"),
        legend.title = element_text(size=15),
        legend.text=element_text(size=15)) 

uniq.plot  # Plot #
```


# 5) Does treatment type affect CFU and morphotype counts?

```{r}
# Rpf effect on CFU #  
neg.cfu.aov <- aov(stdCFU ~ Treatment, data=cfu)
summary(neg.cfu.aov)
TukeyHSD(neg.cfu.aov)

# Rpf effect on morphotype # 
neg.morp.aov <- aov(stdMorph ~ Treatment, data=cfu)
summary(neg.morp.aov)
TukeyHSD(neg.morp.aov)
```




