---
title: "RpfCommunity-AbundanceDiversity"
author: "Venus Kuo"
date: "June 8th, 2017"
output: pdf_document
---

## 1) Questions

We test whether a concentration gradent of Rpf can affect the diversity and abundance of soil microbial community on agar plates.

## 2) Experiment methods

Soil was extracted from Dunn woods over the course of months, treated to a gradient of Rpf concentrations (umol/L) for 4-5 days before vortexed in pyrophosphate solution and spread plated on R2A-no yeast plates. Colony forming units (CFU) and distinct morphological (unique) colony were counted by eye on plate counter. 

## 3) Set working environment and load packages

```{r setup}
# Set working directory #
rm(list = ls())
getwd()
setwd("C:/Users/Venus/Github/RpfCommunity/data/")

# Require or install packages #
package.list <- c('vegan', 'ggplot2', 'gplots', 'psych', 'corrplot', 'BiodiversityR', 'RColorBrewer') 
for (package in package.list) {
  if (!require(package, character.only=T, quietly=T)) { 
    install.packages(package)
    library(package, character.only=T)
} }
```

## 4) Load and describe data set

cfu.csv : An excel sheet containing R2 agar plate information as follows: Soil collection date, soil plate date, plate count date, date of recombiant Rpf production (See Lennon et al 2017??), concentration of stock Rpf protein (mg/mL), soil (g), Rpf treatment concentration (umol/L), rep number, days plates incubated, colonies counted, unique colony morphologies, IMG file number (pictures located on IU Box under "Rpf-Dose Response" and "Soil Community Plate Pictures"), serial dilution used for plates, volume used to inoculate plate, CFU/mL, (CFU/mL)/soil (g), Log10((CFU/mL)/soil(g)), Unique colonies/ soil (g).  

```{r}
setwd("C:/Users/Venus/Github/RpfCommunity/data/")
# Load cfu.csv dataset #
cfu <- read.csv("soil_cfu.csv",  header=T)
```

## 5) Color code dates of soil collection

See cfu.xlsx or cfu.csv for soil collection dates

```{r}
#Create a custom color scale
#myColors <- brewer.pal(5,"Set1")  # 5 is the number of sampling time points #
#names(myColors) <- levels(cfu$Collection)
#colScale <- scale_colour_manual(name = "Sampling Time Points",values = myColors)
#One plot with all the data
#p <- ggplot(dat,aes(x,y,colour = grp)) + geom_point() # colour = Sampling Time Points will be in aes below to label levels #
cfu <- cfu[1:30, ]
```

## 5) Visualization of hump-shaped relationship by scatter plot 

```{r}
# Colony forming units/ soil (g) with increasing Rpf concentration to soil #
cfu.point <- ggplot(cfu, aes(x=Concentration, y = StdCFU)) + 
  geom_point() #+   # Scatter plot #
  #colScale  # To add the colors for each time point #
  
cfu.plot <- cfu.point +    # Figure editting #
  labs(x=expression(paste("Rpf concentrations (",mu,"mol/L)")), 
       y="(CFU/mL) / Soil (g)") +
  theme_classic() +
  theme(axis.text.y=element_text(colour="black", size=15, margin =margin(0,15,0,0)),
        axis.text.x=element_text(colour="black", size =20, margin =margin(15,0,0,0)),
        axis.title.y = element_text(colour="black", size=20,  margin = margin(0,25,0,10)),
        axis.title.x = element_text(colour="black", size=20,  margin=margin(25,0,0,0)),
        panel.border = element_rect(linetype = "solid", colour = "black", size=3, fill=NA),
        axis.ticks.length = unit(-0.35, "cm"),
        axis.ticks = element_line(size = 1.65, colour="black"),
        legend.title = element_text(size=15),
        legend.text=element_text(size=15)) +
  scale_x_continuous(breaks = round(seq(0, 6, by = 1),1)) +
  annotate("text", x =0.2, y=8005000, label = c("A"), size=12)
cfu.plot   # Plot #

# Unique colony morphology / soil (g) with increasing Rpf concentration to soil #
uniq.point <- ggplot(cfu, aes(x=Concentration, y = StdUC)) + 
  geom_point()  #+ # Scatter plot #
  #colScale  # To add the colors for each time point #

uniq.plot <- uniq.point +   # Figure Editting # 
  labs(x=expression(paste("Rpf concentrations (",mu,"mol/L)")), 
       y="Unique Morphology / Soil (g)") +
  theme_classic() +
  theme(axis.text.y=element_text(colour="black", size=15, margin =margin(0,15,0,0)),
        axis.text.x=element_text(colour="black", size =20, margin =margin(15,0,0,0)),
        axis.title.y = element_text(colour="black", size=18,  margin = margin(0,25,0,10)),
        axis.title.x = element_text(colour="black", size=20, margin=margin(25,0,0,0)),
        panel.border = element_rect(linetype = "solid", colour = "black", size=3, fill=NA),
        axis.ticks.length = unit(-0.35, "cm"),
        axis.ticks = element_line(size = 1.65, colour="black"),
        legend.title = element_text(size=15),
        legend.text=element_text(size=15)) +
  scale_x_continuous(breaks = round(seq(0, 6, by = 1),1)) +
  annotate("text", x =0.1, y=30, label = c("B"), size=12)
uniq.plot  # Plot #
```

# Generalized Linear Models # 

```{r}
# Poisson Regression # 
# Used when predicting an outcome variable representing counts from a set of continuous predictor variables #
fit.cfu <- glm(StdCFU~Concentration,data=cfu,family=quasipoisson())
summary(fit.cfu)

fit.uc <- glm(StdUC~Concentration,data=cfu,family=poisson())
summary(fit.uc)
```







