---
title: "RpfCommunity-Figure2"
author: "Venus Kuo"
date: "June 8, 2017"
output: html_document
---
## 1) Questions

We test whether soil bacterial strains display dose-dependency to Rpf protein. We hypothesize that Rpf can affect soil microbial activity. 

## 2) Experiment methods

Kellogg Biological Station (KBS) soil bacterial isolates were grown to late-stationary phase (~2 months) starting on April 29th, 2017. The KBS strains were washed 3x in phosphate buffered solution (PBS) and spread plated on R2A-no yeast plates with varying concentrations of recombinant Rpf protein applied directly on top of plates. Relative biomass was determined from plate pictures on Adobe Photoshop cc (2016). 

## 3) Set working environment and load packages

```{r setup}
# Set working directory #
rm(list = ls())
getwd()
setwd("~/../Github/DormancyGPCA/data/")

# Require or install packages #
package.list <- c('vegan', 'ggplot2', 'gplots', 'BiodiversityR', 'RColorBrewer') 
for (package in package.list) {
  if (!require(package, character.only=T, quietly=T)) { 
    install.packages(package)
    library(package, character.only=T)
} }
```

## 4) Load and describe data set

KBSRelativebiomass.csv :  A excel file that contains the following information about KBS strain spread plated on R2A plates: IMG_file name, Date of plating, KBS strain number, Rpf treatment concentration, Rep number, Days the plates were incubated, colony biomass pixel, total plate biomass, relative biomass of colony growth over total plate biomass. 

```{r}
setwd("C:/Users/Venus/Github/GPCARpf/data/")
# Load cfu.csv dataset #
biomass <- read.csv("KBSRelativebiomass.csv",  header=T)
biomass$KBS_strain <- as.factor(biomass$KBS_strain)
biomass <- na.omit(biomass)
```

## 5) Color code each KBS strain dose-response curve

Black = KBS0714
Green = KBS0812
Red = KBS0701
Orange = KBS0711
Purple = KBS0706

```{r}
#Create a custom color scale
myColors <- brewer.pal(5,"Set1")  # 5 is the number of sampling time points #
names(myColors) <- levels(biomass$KBS_strain)
colScale <- scale_colour_manual(name = "KBS_strain", values = myColors)
#One plot with all the data
#p <- ggplot(dat,aes(x,y,colour = KBS Strains)) + geom_point() # colour = Sampling Time Points will be in aes below to label levels #
```

## 5) Visualization of KBS relative biomass by scatter plot 

```{r}
# Colony forming units/ soil (g) with increasing Rpf concentration to soil #
dose <- ggplot(biomass, aes(x=Treatment, y = Relative_biomass, colours = KBS_strain)) +    # Scatter plot #
  geom_point() # To add the colors for each time point #

  
dose.plot <- dose +    # Figure editting #
  labs(x=expression(paste("Rpf concentrations (",mu,"mol/L)")), 
       y="Relative biomass on Plates") +
  theme_classic() +
  theme(axis.text.y=element_text(colour="black", size=15, margin =margin(0,15,0,0)),
        axis.text.x=element_text(colour="black", size =20, margin =margin(15,0,0,0)),
        axis.title.y = element_text(colour="black", size=20,  margin = margin(0,25,0,10)),
        axis.title.x = element_text(colour="black", size=20,  margin=margin(25,0,0,0)),
        panel.border = element_rect(linetype = "solid", colour = "black", size=3, fill=NA),
        axis.ticks.length = unit(-0.35, "cm"),
        axis.ticks = element_line(size = 1.65, colour="black"),
        legend.title = element_text(size=15),
        legend.text=element_text(size=15)) + 
  colScale
  #scale_x_continuous(breaks = round(seq(0, 6, by = 1),1)) +
  #annotate("text", x =0.2, y=10, label = c("A"), size=12)
dose.plot   # Plot #
```

## 6) Line graph of Rpf dose-dependent biomass response

```{r}



```







